---
title: "Segregation Classification"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
#25 aug '23 based on 9-10-19; for github
#9-10-19 based on 5-24-19_accuracyplots and 5-22-19_sim
#Point is just to make and plot a binary and a clustered neighborhoods, using colors

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)  #quick and dirty way to suppress warnings
#Preamble from 9-10-19 website plots
library(ggplot2)
library(tidyr)
library(plyr);library(dplyr, warn.conflicts = F)
library(tictoc)
library(stargazer)
rm(list=ls())
s = function(x){summary(factor(x))}
####################################################################################################
```

## Relevant social science problem

We would like a method for classifying neighborhoods as **segregated** or not. This is a problem with many real-world applications in social science.

We will do this by generating simulated neighborhoods and using them to test classifiers.

First we set some global parameters: the size of the neighborhood (arbitrary units, could be meters) and the number of grid spaces.

```{r Global parameters}

####################################################################################################
#Set global parameters
xlim = 100 #neighborhood size x. call this meters. or km if this is city scale??
ylim = 100 #neighborhood size y. call this meters. or km if this is city scale??
ngrid = 10 #number of grid spaces
####################################################################################################
```

## Two functions to create simulated neighborhoods

We will use two data-generating processes (DGP's): binary and cluster. These can both be used to create segregated or integrated (non-segregated) neighborhoods. 

Neighborhoods generated using the binary DGP are split at a particular line of longitude (i.e. left vs right), without loss of generality. In segregated neighborhoods, individuals from the minority group are more likely to be found to the east (right) of the line. 

### Binary DGP

This is a function to create a segregated neighborhood using the binary DGP. Individuals from the minority group are concentrated in the eastern part of the neighborhood. The concentration parameter <code>conc</code> determines <i>how segregated</i> the neighborhood is, i.e. the probability that a particular individual will live on the side of the neighborhood that "belongs" to their group. 

**Here is a Shiny app that demonstrates the binary DGP and its parameters:** <https://jeremyspater.shinyapps.io/app-2/>.

```{r Binary DGP}
####################################################################################################
#Binary segregation

#Nonsegregated neighborhoods: just a uniform distribution
create_Nonseg = function(n, xlim, ylim, pminority){
  fr = data.frame(long = runif(n,0,xlim),
                  lat = runif(n,0,xlim),
                  minor = rbinom(n,1,pminority) == 1)
  return(fr)
}

#Seg neighborhoods: Assume that majority is uniform across whole space

create_Seg = function(n, xlim, ylim, pminority, conc){ #concentration parameter
  fr = data.frame(minor = rbinom(n,1,pminority) == 1,
                  long = NA,
                  lat = NA,
                  ghe = rbinom(n,1,conc)) #"ghetto" parameter: proportion of each group on the "correct" side
  #lat longs for majority (not concentrated), ie ghe = F
  fr$long[fr$minor == F & fr$ghe == F] = runif(sum(fr$minor == F & fr$ghe == F), 0, xlim) #x: runif from 0 to xlim
  fr$lat[fr$minor == F & fr$ghe == F] = runif(sum(fr$minor == F & fr$ghe == F), 0, ylim) #y: runif from 0 to ylim
  #lat longs for majority (concentrated)
  fr$long[fr$minor == F & fr$ghe == T] = runif(sum(fr$minor == F & fr$ghe == T), min = 0, #x: runif from 0 to ghetto limit
                                               max = (1 - pminority)*xlim) #ghetto limit: proportional to size of majority
  fr$lat[fr$minor == F & fr$ghe == T] = runif(sum(fr$minor == F & fr$ghe == T), 0, ylim) #y: runif from 0 to xlim
  #lat longs for minority (not concentrated)
  fr$long[fr$minor == T & fr$ghe == F] = runif(sum(fr$minor == T & fr$ghe == F), 0, xlim) #x: runif from 0 to xlim
  fr$lat[fr$minor == T & fr$ghe == F] = runif(sum(fr$minor == T & fr$ghe == F), 0, ylim) #y: runif from 0 to ylim
  #lat longs for minority (concentrated)
  fr$long[fr$minor == T & fr$ghe == T] = runif(sum(fr$minor == T & fr$ghe == T),  #x: runif from ghetto edge to xlim
                                               min = (1-pminority)*xlim, max = xlim) #ghetto limit: prop. to size of minority
  fr$lat[fr$minor == T & fr$ghe == T] = runif(sum(fr$minor == T & fr$ghe == T), 0, ylim) #y: runif from 0 to ylim
  return(fr)
}
```
This code creates a binary-segregated neighborhood and makes a plot.
```{r Make and plot binary neighborhood}
#make one and plot
d = create_Seg(n = 10000, xlim = 100, ylim = 100, pminority = 0.3, conc = 0.8) %>% rename(Ethnicity = minor) %>%
  mutate(Ethnicity = mapvalues(Ethnicity, from = c('TRUE', 'FALSE'), to = c('Minority','Majority')))

ggplot(data = d) + geom_point(aes(x = long, y = lat, color = Ethnicity), size = 2) + theme_bw() +
  ggtitle('Binary segregation example') + theme(text = element_text(size=24), plot.title = element_text(hjust = 0.5)) +
  scale_shape_manual(values = c(1, 2)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(), 
        panel.background = element_rect(fill = "grey")) +
  scale_color_manual(values=c("darkmagenta", "green4")) +
  xlim(0,100) + ylim(0,100)
path0 = paste0('/Users/jeremyspater/Dropbox/duke/political economy core/prospectus/methods paper/results_output/',Sys.Date(),'/')
dir.create(path0)
#ggsave(filename = paste0(path0, 'binary_seg_example_website.png'), height = 200, width = 200, units = 'mm'); rm(path0)
```

### Cluster DGP

In neighborhoods generated using the cluster DGP, individuals are located in circular clusters that are situated randomly throughout the neighborhood. In segregated cluster neighborhoods, each cluster is predominantly made up of individuals from one group or the other (majority or minority). 

The cluster DGP generates circular clusters of individuals within the neighborhood. For segregated neighborhoods, each cluster consists predominantly of individuals from one group, while for integrated neighborhoods, clusters are not segregated by group.

**Here is a Shiny app that demonstrates the binary DGP and its parameters:** <https://jeremyspater.shinyapps.io/app-cluster/>.

```{r Clustered DGP}
####################################################################################################
#Clustered process

library(spatstat)

#https://rdrr.io/cran/spatstat/man/rPoissonCluster.html
# multitype Neyman-Scott process (each cluster is a multitype process)
#[This is same as Matern cluster process, only with marks?]
nclust2 <- function(x0, y0, radius, n, types=c("yes", "no"), p) {
  X <- runifdisc(n, radius, centre=c(x0, y0))
  #M <- sample(types, n, replace=TRUE, prob = c(p, 1-p)) #this just makes the marks random
  M <- sample(types, 1, replace=TRUE, prob = c(p, 1-p)) %>% rep(n)#this gives everybody in the cluster the same mark
  marks(X) <- M
  return(X)
}

#Nonsegregated version: Type is NOT by cluster
nclust1 <- function(x0, y0, radius, n) {
  X <- runifdisc(n, radius, centre=c(x0, y0))
  return(X)
}

ClusterSeg = function(n_samp = 100, p = 0.3, nclus = 13, ka = 0.05, r = 3){
  kids = rPoissonCluster(kappa = ka, #determines number of clusters
                         expand = 10, #expansion window for parents (so cluster center can be offscreen)
                         rcluster = nclust2, #function for generating clusters, above
                         radius = r,#3, #tried 10, but the clusters overlap too much. Size of cluster
                         n = nclus, #tried 5, but it didn't look very segregated. Number in cluster
                         p = p, #prob of minority
                         win = owin(c(0,100),c(0,100))) #limits of window
  
  kids_df = data.frame(long = kids$x,
                       lat = kids$y,
                       minor = kids$marks) 
  ns = min(nrow(kids_df), n_samp)
  return(kids_df[sample(nrow(kids_df), ns), ]) #return sample of n rows
}

ClusterNonSeg = function(n_samp = 100, p = 0.3, nclus = 13, ka = 0.05, r = 3){
  kids = rPoissonCluster(kappa = ka, #determines number of clusters
                         expand = 10, #expansion window for parents (so cluster center can be offscreen)
                         rcluster = nclust1, #function for generating clusters, above
                         radius = r,#3, Size of cluster
                         n = nclus, #Number in cluster
                         #p = p,
                         win = owin(c(0,100),c(0,100))) #limits of window
  
  marks(kids) = sample( c('yes', 'no'), kids$n, replace=TRUE, prob = c(p, 1-p)) #select marks; not by cluster (because nonseg). Determines majority/minority
  
  kids_df = data.frame(long = kids$x,
                       lat = kids$y,
                       minor = kids$marks) 
  ns = min(nrow(kids_df), n_samp)
  return(kids_df[sample(nrow(kids_df), ns), ]) #return sample of n rows
}
```
This code creates a cluster-segregated neighborhood and makes a plot.
```{r Make and plot (clustered)}
#make one and plot
d = ClusterSeg(ka = 0.01, nclus = 100, r = 10, p = 0.4, n_samp = 1E6) %>% rename(Ethnicity = minor) %>%
  mutate(Ethnicity = mapvalues(Ethnicity, from = c('yes', 'no'), to = c('Minority','Majority')))

#ggplot(data = d) + geom_point(aes(x = long, y = lat, shape = Ethnicity), size = 2) + theme_bw() +
ggplot(data = d) + geom_point(aes(x = long, y = lat, color = Ethnicity), size = 2) + theme_bw() +
  ggtitle('Cluster segregation example') + 
  theme(text = element_text(size=24), plot.title = element_text(hjust = 0.5)) +
  scale_shape_manual(values = c(1, 2)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background = element_rect(fill = "grey")) +
  scale_color_manual(values=c("darkmagenta", "green4")) +
  xlim(0,100) + ylim(0,100)

path0 = paste0('/Users/jeremyspater/Dropbox/duke/political economy core/prospectus/methods paper/results_output/',Sys.Date(),'/')
dir.create(path0)
#ggsave(filename = paste0(path0, 'cluster_seg_example_website.png'), height = 200, width = 200, units = 'mm'); rm(path0)
```
